\section{Automated Trading Systems}
	Automated trading systems are widely used in financial markets and allow the trader to establish specific rules for:
	
	\begin{itemize}
		\item Which markets to trade.
		\item The price and type of trades to place in a market.
	\end{itemize}
	
	Automating the trading of markets offers many benefits compared to manual trading including:
		
	\begin{itemize}
		\item Minimising emotions - a trader maybe affected by emotions and disregard their rules either because they are unsure about entering a trade or because they are reluctant to exit one. 
		\item Achieve consistency - if a trader does not follow their rules it is hard to compare progress over time.
		\item Improve order entry speed - computers may respond to changing market conditions and place and cancel orders faster than a human.
		\item Trade a wider range of markets - computers can process information and trade over a wider range of markets simultaneously compared to a human.
		\item Ability to Backtest - an automated trading strategy can be tested on historical markets to see how well it would have performed, providing an indication of future performance.
	\end{itemize}
	
	To aid automation of trading on Betfair's markets the trader should be able to predict the outcome of an event or the direction in which the price will move.\\
	
	Both technical and fundamental analysis are used to predict the future price movement of financial markets. Technical analysis concentrates on the study of market action by looking a the previous price movement of a security. Fundamental analysis focuses on the economic forces of supply and demand that cause prices to move higher, lower, or stay the same\cite{murphy1999technical}.\\
	
	When applied to a sporting event such as a horse race fundamental analysis would look at factors such as:
	\begin{itemize}
		\item How the horse performed previously.
		\item How the jockey performed previously.
		\item The distance of the race.
		\item The condition of the race course.
	\end{itemize}	
	 
	 In contrast technical analysis looks at how the price and betting activity in the market had evolved and how that compared to previous markets.
	
	