\section{Project Objectives}

This project will be split into two sections: 
	
	\begin{itemize}
		\item The first section will focus on designing and building a computer trading system for the Betfair exchange through which the user can action trades manually and run a predefined automated trading strategy on a given market.
		\item The second section will focus on applying machine learning techniques to historical market data to design and build a model that can be used as an indicator by an automated trading strategy.
	\end{itemize}

\subsection{First section objectives}

	\begin{itemize}
		\item Write a trading system for the Betfair exchange that can:
			\begin{itemize}
				\item Retrieve and store market data from the Betfair exchange concurrently over multiple markets.
				\item Place, cancel and amend orders at the Betfair exchange concurrently over multiple markets.
				\item Track and broadcast the state of orders the system has placed at the Betfair exchange.
				\item Track metrics concurrently over multiple markets.
				\item Track a users position concurrently over multiple markets.
				\item Record market data and trading activity to allow the user to review it at a later date.
				\item Follow and action a predefined trading strategy.
			\end{itemize}
		\item Write a GUI for the trading system that should allow the user to:
			\begin{itemize}
				\item Navigate markets on the exchange.
				\item View market information in real time.
				\item Manually action trades.
				\item Action a predefined trading strategy on a given number of markets.
				\item Review and compare historical market and trading data.
			\end{itemize}
	\end{itemize}

\subsection{Second section objectives}

	\begin{itemize}
		\item Analyse historical exchange data and select a machine learning model to use on the data.
		\item Train, optimise and test the chosen model using the historical data.
		\item Report on the results produced when testing the model. 
		\item Integrate the trained model into the trading system built in the first section of the project.
		\item Write a trading strategy that uses the model to make decisions and report on its success.
	\end{itemize}		
	
\subsection{Changes in the objectives from the interim report}

The interim report included the following objectives which have not been included in the final report:

	\begin{itemize}
		\item Define a language so a user can describe a trading strategy.
		\item Write a parser or compiler to convert a trading strategy written in the above language into steps the trading system can understand.
		\item Create trading strategies of differing complexities and test and report on their performance.
	\end{itemize}
	
As the project progressed these objectives were sidelined in favour of placing more emphasis on the machine learning section of the project which was only listed as an extended objective in the interim report.