\section{Project Objectives}
	This project has two parts, to build a trading system for the Betfair Exchange and to train a model that can be used to predict price trends on Betfair markets.

	\subsection{Part 1}
	The primary objectives are to build a trading system that can be used to:
	
	\begin{itemize}
		\item Navigate markets on the Betfair Exchange.
		\item Manually trade markets on the Betfair Exchange.
		\item Automate the trading of markets on the Betfair Exchange.
	\end{itemize}

	The secondary objectives are to add functionality to:
		
	\begin{itemize}
		\item Record market data and trading activity to be analysed after the fact.
		\item Provide a framework to back-test an automated trading strategy against recorded market data.
	\end{itemize}

	The trading system should include a graphical user interface (GUI). The GUI design however is not the focus of this project and the emphasis will be on adding functionality to the trading system rather than the design aspects of the user interface.\\
	
	This part of the project will not be concerned with the resiliency or security of the trading system. These are complex subjects and outside the scope of this project.
			
	\subsection{Part 2}
	The primary objectives are to:
	
	\begin{itemize}
		\item Select a machine learning algorithm to be used to build a model from historical market data.
		\item Process the historical market data into intervals and select and apply technical analysis indicators.
		\item Divide the data into sets that can be used to train and test the model.
		\item Optimise the model using the training data.
		\item Analyse the results of the model on the testing data.
	\end{itemize}
	
	The secondary objectives are to:

	\begin{itemize}
		\item Integrate the model into a trading strategy.
		\item Automate the trading strategy using the system built in the first part of this project.
	\end{itemize}	
		
	The primary objectives of both parts of this project are achievable within the time limits. The secondary objectives will only be met if there is enough time after the primary objectives have been met.
	