\chapter{Requirements Analysis}
This section lists brief functional (what the system shall do) and non-functional (how the system shall do it) requirements for each part of the project. Because this is an Agile project this is not an exhaustive list and new requirements will be incorporated as they are discovered during the development process.  

\subsection{Part 1 - Building a Trading System}
The requirements were formed by considering the requirements of a trader and the constraints imposed by the Betfair Exchange's API\cite{betfairAPI}.\\

The requirements of a trader are that they must be able to:

	\begin{itemize}
		\item Navigate markets on the exchange.
		\item Receive real time updates for markets on the exchange.
		\item Place and cancel orders across all markets on the exchange.
		\item Receive real time updates on the status of their orders on the exchange.
		\item Record data for selected markets on the exchange.
		\item Test a trading strategy without placing orders on the exchange.
		\item Action an automated strategy on markets on the exchange.
	\end{itemize}

The constraints imposed by the Betfair Exchange's API are that:

	\begin{itemize}
		\item Navigation data for applications must be retrieved in the form of a compressed file\cite{BetfairNavigationData}.
		\item The exchange must be polled at regular intervals for market data updates.
		\item The exchange must be polled at regular intervals for order updates.
		\item The number of requests for a single market's data must not exceed 5 per second\cite{listMarketBook}.
		\item The amount of data requested in each call to the exchange must be within a maximum weighting\cite{dataRequestLimits}.
		\item Any party making calls to the exchange must first authenticate\cite{loginSessionManagement}.
		\item All subsequent calls to the exchange must contain a session token and application key\cite{ApplicationKeys}.
		\item The exchange provides a service with delayed data for testing but does not allow betting transactions.
	\end{itemize}
		
As a result\\

The functional requirements are the system must:
	\begin{itemize}
		\item Poll the exchange for data on selected markets and notify the user when the data changes.
		\item Place and cancel orders at the exchange.
		\item Poll the exchange for data on the markets with unmatched orders and notify the user when their status changes.
		\item Provide the user with a means to navigate markets on the exchange.
		\item Let the user record data for selected markets.
		\item On request action an automated trading strategy on selected markets.
		\item Let the user test an automated strategy on selected markets.
	\end{itemize}
	
The non-functional requirements are the system must:
	\begin{itemize}
		\item Download Navigation data on start-up.
		\item Authenticate to the exchange on start-up.
		\item Store the session token and application key and apply them to all exchange calls.
		\item Poll the exchange for updates at regular intervals not exceeding 5 calls per second per market.
		\item Group calls to the exchange so that data request limits are not exceeded.
		\item Implement a local order book to simulate the placement of orders in a test environment.
		\item Make and receive calls asynchronously without blocking.
	\end{itemize}
\newpage
\subsection{Part 2 - Building a Predictive Model}
Betfair and their third party data provider Fracsoft supplied one months market data for horse racing markets from the 11th October 2014 to the 10th November 2014 showing sub-second deltas in the market. The requirements were formed by considering the requirements of a trader from a predictive model and by looking at the constraints imposed by the historical data.\\

The requirements of a trader from a predictive model are that it must:
	\begin{itemize}
		\item Produce accurate results
		\item Run in real time
	\end{itemize}

The constraints imposed by the historical Betfair Exchange data are it must:
	\begin{itemize}
		\item Be separated by market (Race) and selection (Runner)
		\item Be grouped into intervals so technical analysis indicators can be applied
		\item Transformed into a format where it can be sorted and rearranged
	\end{itemize}

As a result the functional requirement of the model is that it make accurate predictions and the non-functional that it return predictions in real time.