\chapter{Conclusion}
	The first part of the project has met the primary objectives to build a trading system that can be used to:
	\begin{itemize}
		\item Navigate markets on the Betfair Exchange.
		\item Manually trade markets on the Betfair Exchange.
		\item Automate the trading of markets on the Betfair Exchange.
	\end{itemize}
	
	The the first part of the project has not met the secondary objectives to add functionality to:
	\begin{itemize}
		\item Record market data and trading activity to be analysed after the fact.
		\item Provide a framework to back-test an automated trading strategy against recorded market data.
	\end{itemize}


	The second part of the project has met the primary objectives to:
	\begin{itemize}
		\item Select a machine learning algorithm to be used to build a model from historical market data.
		\item Process the historical market data into intervals and select and apply technical analysis indicators.
		\item Divide the data into sets that can be used to train and test the model.
		\item Optimise the model using the training data.
		\item Analyse the results of the model on the testing data.
	\end{itemize}
	
	The second part of the project has not met the secondary objectives to:
	\begin{itemize}
		\item Integrate the model into a trading strategy.
		\item Automate the trading strategy using the system built in the first part of this project.
	\end{itemize}	
	
	Appendix ~\ref{appendix:futureWork} contains a list of issues raised during the development process to be implemented as future work.\\
	
	Additionally the predictive model needs to be integrated into the trading system to test its accuracy on a live market. At the moment the results only show its accuracy on predicting individual intervals. A true test of the model would be to incorporate it into a strategy that included:
	\begin{itemize}
		\item Thresholds for stopping out losing trades.
		\item Thresholds for how much profit to take on winning trades.
		\item How many successive Up or Down indicators are required for a trade to be actioned.
	\end{itemize}
	The accuracy of the predictive model could be improved by:
	\begin{itemize}
		\item Changing the technical analysis indicators used as features.
		\item Experimenting with different combinations features and changing the number of features used.
		\item Using regression as opposed to classification, outputting real numbers showing the predicted probability that a market will trend up, down or stay the same.
		\item Comparing the results of other machine learning algorithms such as a Support Vector Machine or Multi layer Perceptron to see if they better suit the data.
	\end{itemize}
		
	\section{Development Approach}
	\subsubsection{Agile}
	The Agile approach to development has worked well. Implementing requirements in small iterative cycles ensured consistent progress during development.
	
	\subsubsection{Testing}
	The focus on continuous testing ensured that each commit didn't beak the build. Using Git and SBT to track and manager files and builds was very effective. Due to time constraints there are areas of the code that still need testing. This was a result of trying to balance the speed of development with the level of testing to ensure the project's primary objectives were met. Issues have been raised for each section and are in Appendix~\ref{appendix:futureWork}.\\
	